Coherent optical association of a single molecule

### 2020-10-23 paper.tex
Remote notes..
fig3 update
Legend for inset

\begin{figure*}[t!]
  \includegraphics[width=\textwidth]{fig3.pdf}
  \caption{
    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
    with loss on the atom and molecule state. The combined fit is used to determine
    both the Raman Rabi frequency and the loss rates.
    (B) \todo{inset?} Two-body atom lifetime in $15 \mathrm{mW}$ of trap depth caused by
    off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.1990(90) \mathrm{ms}$
    measured from the Raman transition data.
    The oscillation in the survival is the result of the interference
    between the two Raman pulses with incomplete transfer.
    \label{f-lifetime}}
\end{figure*}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{fig4.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (A) The light shift of the Raman resonance scales as $P_{tweezer}$
    and follows $1/\Delta$ with an offset.
    The fit also includes a small term that is proportional to $P_{tweezer}^2$
    which is caused by the effective magnetic field generated by the tweezer which is
    perpendicular to the real magnetic field.
    (B) Raman Rabi frequency ($\Omega_R$) scales as $P_{tweezer}^{1.29}$
    and follows $1/\Delta$ with an offset.
    From these results we can confirm the theory prediction of
    the atom-molecule matrix element ratio.
    (C) Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
    this is consistent with a two photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    \label{f-det}}
\end{figure*}

@@

Lastly, to confirm that the excess scattering does not come from the atomic state,
we measure the two-body scattering rate
without turning on the second frequency (Fig.~\ref{f-det}C).
The scattering rate scales as $P_{tweezer}^{2.58}$ which is inconsistent
with a single photon scattering process.
We have not been able to observe a dependency on the detuning in order to verify
if the scattering process is related to the $v'=0$ state,
but the power scaling strongly suggests the existence of a unknown two photon scattering process.
Nevertheless, the absolute scattering rate is much lower than the total scattering rate
and is not the limiting factor in our experiment.

@@

% Shift figure 4 x axis
% Try to move 3C forward
% Inset in 4AB
% Inset in 2C (3A) (or as a separate figure)
% Maybe remove 3A (move into supplemental material)
% Arrow head for molecule overlaps the datapoint
% 4C as inset to 2B

>>>>

\begin{figure}[t!]
  \includegraphics[width=0.48\textwidth]{fig3.pdf}
  \caption{
    (A) Fitting of Raman detuning scans at different times to a model of Raman transition
    with loss on the atom and molecule state. The combined fit is used to determine
    both the Raman Rabi frequency and the loss rates.
    (B) Two-body atom lifetime of $5.1(11) \mathrm{ms}$
    in $15 \mathrm{mW}$ of trap depth caused by off-resonance photoassociation.
    This is used to improve the fitting of the Raman transfer data.
    Inset: Atomic scattering rate scales as $P_{tweezer}^{2.58}$,
    this is consistent with a two photon scattering process.
    We have not measured a clear dependency of the loss rate on the tweezer detuning.
    (C) Direct measurement of molecule lifetime in $15 \mathrm{mW}$ of trap depth.
    Molecule survival is detected by dissociating back to atoms using a second Raman transition.
    The lifetime is consistent with the $0.1990(90) \mathrm{ms}$
    measured from the Raman transition data.
    The oscillation in the survival is the result of the interference
    between the two Raman pulses with incomplete transfer.
    \label{f-lifetime}}
\end{figure}

@@

\begin{figure*}
  \includegraphics[width=\textwidth]{fig4.pdf}
  \caption{Raman transition parameters as a function of tweezer and Raman power and detuning.
    (A) The light shift of the Raman resonance scales as $P_{tweezer}$
    and follows $1/\Delta$ with an offset.
    The fit also includes a small term that is proportional to $P_{tweezer}^2$
    which is caused by the effective magnetic field generated by the tweezer which is
    perpendicular to the real magnetic field.
    (B) Raman Rabi frequency ($\Omega_R$) scales as $P_{tweezer}^{1.29}$
    and follows $1/\Delta$ with an offset.
    From these results we can confirm the theory prediction of
    the atom-molecule matrix element ratio.
    \label{f-det}}
\end{figure*}

@@

Lastly, to confirm that the excess scattering does not come from the atomic state,
we measure the two-body scattering rate
without turning on the second frequency (Fig.~\ref{f-lifetime}B inset).
The scattering rate scales as $P_{tweezer}^{2.58}$ which is inconsistent
with a single photon scattering process.
We have not been able to observe a dependency on the detuning in order to verify
if the scattering process is related to the $v'=0$ state,
but the power scaling strongly suggests the existence of a unknown two photon scattering process.
Nevertheless, the absolute scattering rate is much lower than the total scattering rate
and is not the limiting factor in our experiment.

@@
